Staged Abstract Interpreters

### 2019-02-28 paper/10_intro.tex
misc

\begin{itemize}
  \item We progressively present a unifying construction that naturally extends the
    first Futamura projection to abstract interpreters. Starting from a generic
    interface of the interpreter for a tiny functional language
    (Section~\ref{generic_if}), we first show the instantiation of concrete
    interpretation in Section~\ref{unstaged_conc}. Then we lift it to the staged
    version by adding stage annotations to the semantic operations
    (Section~\ref{stagedinterp}); and to the abstract interpreter by applying
    abstraction to the environment, store, and values. Finally, we show the
    combination of the two transformations, dubbed \textit{staged abstract
    interpreters}, can be easily derived (Section~\ref{sai}).

  \item \todo{modular analysis} As shown in Section~\ref{sai}, we demonstrate
    that if we apply the abstract interpreters on open programs, it not only
    improves the \textit{efficiency} but also the \textit{scalability}, which are
    two major issues in static analysis.

  \item In Section~\ref{cases_study}, we conduct three case studies to
    demonstrate the applicability and usefulness of the proposed approach to
    specialize analyses.
    (1) We first revisit the Abstract Compilation (AC)
    \cite{Boucher:1996:ACN:647473.727587} technique in Section~\ref{cs_ac}.
    Our approach and AC are able to achieve the same goal, however, as we show,
    one of the advantage of staging through types is it does not require
    whole-analyzer refactoring.
    (2) We extend the staged abstract interpreter shown in Section~\ref{sai} to
    two variants of control-flow analysis: context-sensitive pushdown
    control-flow analysis and \todo{precise-store?}.
    (3) In Section~\ref{cases_imp}, we plug a \note{staged numerical domain}
    \todo{widening} into the staged abstract interpreter, demonstrating that a
    numerical analysis on imperative languages can be also implemented and
    speeded-up in this manner.

>>>>

\begin{itemize}
  \item We progressively present a unifying construction that naturally extends
    the first Futamura projection to abstract interpreters. Starting from a generic
    interface of the interpreter for a small functional language
    (Section~\ref{generic_if}), we first show the instantiation of concrete
    interpretation (Section~\ref{unstaged_conc}). Then we lift it to the staged
    version by replacing the binding-time type (Section~\ref{stagedinterp}); and to
    the abstract interpreter by applying abstraction to the environment, store, and
    values (Section~\ref{unstaged_abs}). Finally, we show the combination of the two
    transformations, dubbed \textit{staged abstract interpreters}, can be easily
    derived (Section~\ref{sai}).

  \item We demonstrate that if we apply the abstract interpreter on components
    of the program separately, it not only improves the \textit{efficiency} but
    also the \textit{scalability} (Section~\ref{sai} \todo{}), which are two
    major issues in static analysis.

  \item We conduct two case studies to show the applicability and usefulness
    of applying meta-programming to static analysis (Section~\ref{cases_study}).
    (1) We first revisit the Abstract Compilation (AC)
    \cite{Boucher:1996:ACN:647473.727587} technique (Section~\ref{cs_ac}).
    Our approach and AC are able to achieve the same goal, however, as we show,
    one of the advantage of staging through types is it does not require
    whole-analyzer refactoring.
    (2) We extend the staged abstract interpreter to two variants of
    control-flow analysis: context-sensitive pushdown control-flow analysis and
    \todo{precise-store?} (Section~\ref{sai}).
